---
title: "M2P2 - Predict"
author: "NF"
date: "11-10-2019"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

# Title

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Summary of assignment

Investigate if *customer responses* to some survey questions (e.g. income, age, etc.) enable us to predict the answer to the brand preference question in order to choose a brand to partner with for future business developments. If so, then make predictions and provide the sales team with a complete view of **what brand our customers prefer**.

## data sets used

A file with complete responses is used as data set to train Supervised Machine Learning models to build a predictive model. A file with survey responses without brand preference is used as main test set to apply the optimized model (*C5.0*) to predict the brand preference. 


```{r libraries}
library(readr)
library(caret)
library(kableExtra)
library(knitr)
```

```{r load data}
CompleteResponses <- read_csv(
  "CompleteResponses.csv",
  col_types = cols(
    brand = col_factor(levels = c("0","1")),
    zipcode = col_factor(levels = c("0","1", "2", "3", "4", "5", "6", "7","8"))
    )
  )

NewIncom <- read_csv("SurveyIncomplete.csv")
```

# Pre process

## Preprocessing of data in a way that it can be used for modelling

While importing data with function "Import Dataset" the columns "elevel", "cars", "zipcodes" and "brand" were converted to factor. "brand" and "zipcode" within the wizard and "cars" and "elevel" using the as.factor function.

```{r Set to factor, include=FALSE}
CompleteResponses$car <- as.factor(CompleteResponses$car)
CompleteResponses$elevel <- as.factor(CompleteResponses$elevel)
```

Furthermore the data is checked for missing values and renamed to create a new working file.

```{r Check missing values and view, include=FALSE}
is.na(CompleteResponses)
ComResp <- CompleteResponses
```

Consequently the working data file views as below and has 9898 rows.We can see that we have a large range of different salaries between 20k to 150k, ages between 20 to 80, 5 levels of education, 20 different types of cars the respondents drive and a representation of respondents from 8 different regions. Reading the brandpreference values it suggests a slightly higher preference for brand 1 (Mean = 62%) being Sony and compared to brand 0 Acer. 

```{r Show Data str}
library(readr)
exampledata <- read_csv("C:/Users/NFortuin/Desktop/Ubiqum/Modules/Module 2/M2P2 Predict/M2P2 - Predict/CompleteResponses.csv")
kable(head(exampledata)) %>% 
  kable_styling()
```

## Define impactful attributes to select relevant features for prediction

To determine which attributes within the available dataset are impactful to predict brand preference among customers the function VarImp from R is used.

```{r Rank Important attributes}
RankImp <- readRDS("RankImp.rds")
```

Based on the outcome Age and Salary are considered relevant for predicting brand preference among customers that have not expressed their brand preference yet.

## Created a new dataframe with only impactful attributes to train and test models

After selection of the two impactful attributes (age & salary) a new dataframe was created as new working file.

```{r Dataframe age, salary, brand}
dfnew <- CompleteResponses[,c(1,2,7)]
ComResp <- dfnew
```

## Splitted data (sample) and trained and tested it with Model C5.0

For this model the parameters tunelength was set to 2 and the data was centered en scaled based on the median and standard deviation in the dataset. The model gave an almost perfect performance indicator for Accuracy (89%) and a substantial Kappa of (77%). 
``````{r Train, Test Model C5.0}
rfFit <- readRDS("rfFit.rds")
```

## Compared the outcomes on performance if model K-NN is used

For this model the parameters tunelength was set to 1 and the data was centered en scaled based on the median and standard deviation in the dataset. The model gave an almost perfect performance indicator for Accuracy (90%) and a substantial Kappa of (79%). 

```{r}
rfFit2 <- readRDS("rfFit2.rds")
```

# Machine learning process

## Model Random Forest

For this model the parameters tunelength was set to 1 and the data was centered en scaled based on the median and standard deviation in the dataset. The model gave a almost perfect performance indicators for Accuracy (91%) and a almost perfect Kappa of (80%). 

```{r}
rfFit3 <- readRDS("rfFit3.rds")
```

## Model ADAboost

For this model the parameters tunelength was set to 1 and the data was centered en scaled based on the median and standard deviation in the dataset. The model gave an almost perfect performance indicator for M1.Accuracy (91%) and a substantial Kappa of (78%). The resampling results for 'Real Adaboost' for Accuracy are 90% and for Kappa 79%. 

```{r}
rfFit4 <- readRDS("rfFit4.rds")
```

For all the models the accuracy is considered good and the Kappa substantial. 

# Imported and preprocessed incomplete survey results

To excute the prediction the survey results without brand preference is load and preprocessed in the same way as the original survey. After that a new datafile was created as working file named NewIncom

```{r}
NewIncom
```

# Predict brand preference for Acer or Sony

Because all models showed a good performance all models are used to do a prediction for brand preference. 

Therefore all models have been used for predicting brand preference among responsdents of the customers survey that have not expressed their brand preference.  

For all models the Accuracy was moderate but the best for C5.0 (0.3864). The Kappa in all cases was 0.0 because the calculation of the reliability of the outcome based on coincidence is based on 0 (brand preference in original file). 

Incom$brand_pred <- predict(object = rfFit, newdata = Incom) cleary showed that 60% are expected to have a preference for Brand 1 being Sony. 

# plotted the results of the prediction in different plots

The predictions of the C5.0 were plotted in different plots. The relevant ones that best show the brand preference are shown below.

```{r}
library(ggplot2)
#Original data scatterplot----
ggplot(data = CompleteResponses) +
  geom_point(aes(x = age, y = salary, col = brand)) +
  labs(title = "Scatterplot complete data", subtitle = "brandpreference per age group")
ggsave("plotagevssalary_col_brand.png", width = 5, height = 5)
```


Scatterplot of predicted data

```{r}
# add prredictions incomplete dataset
NewIncom$brand_pred <- predict(object = rfFit, newdata = NewIncom)

# plot results
ggplot(data = NewIncom) +
  geom_point(aes(x = age, y = salary, col = brand_pred)) +
  labs(title = "Scatterplot predicted data", subtitle = "brandpreference per age group")


ggsave("plotagevssalary_col_brand_pred.png", width = 5, height = 5)
```
# Conclusion
Sony is the best partner to build business in the future because it is expected to have the preference of most of our customers. These customers have in general a higher salary and age. Only in the age where customers are having upgrowing kids Acer is also an appreciated brand. 
